API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex

Over the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications, successes in various machine learning
challenges (e.g., Kaggle), or significant statistics derived from our
repositories and mailing list.  At the time of writing, the project is watched
by 1309 people and forked 667 times on GitHub; the mailing list receives
more than 300 mails per month; and version control logs
% ddaa494c116e3c16bf032003c5cccbed851733d2
show 183 unique contributors to the codebase.

@@

\section{Future Work}
\label{sec:future_work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Topics like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

>>>>

Over the past few years, the project has proved valuable to an ever increasing
user base. Its popularity can be gaged from various indicators such as hundreds
of citations in scientific publications, successes in various machine learning
challenges (e.g., Kaggle), or significant statistics derived from our
repositories and mailing list.  At the time of writing, the project is watched
by 1309 people and forked 667 times on GitHub; the mailing list receives more
than 300 mails per month; version control logs
% ddaa494c116e3c16bf032003c5cccbed851733d2
show 183 unique contributors to the codebase and the online documentation
website receives 37k unique visitors and 295k page views per month.

@@

\section{Future Work}
\label{sec:future_work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Tasks like structured prediction or reinforcement learning are
considered off-scope for the project, since they would require quite different
data representations and APIs.
